### 2018-08-28 analysis-note-vf/Appendix.tex
update the analysis note

\chapter{Binning the incoherent DVCS data to match the free proton DVCS 
published data}

@@

\begin {table}[!h]
\begin{center}
\begin{tabular}{|l|l|l|l|l|l|l|l|}
\hline
<$x_{B}$> & <$Q^2$> & <-t> & $\alpha$ & $\Delta \alpha$ &  $\beta$ & $\Delta 
   \beta$ & $\chi^{2}$\\
\hline
0.238  & 1.89 & 0.14 & 0.243 & 0.013 & -0.02 & 0.09 & 1.0\\
\hline
0.249  & 1.95 & 0.28 & 0.275 & 0.014 & -0.06 & 0.09 & 1.3\\
\hline
0.249  & 1.95 & 0.49 & 0.200 & 0.026 & -0.36 & 0.15 & 1.3\\
\hline
0.248  & 1.94 & 0.77 & 0.172 & 0.035 & 0.01 &  0.31 & 0.3\\
\hline
\end{tabular}
   \caption{Free proton DVCS published asymmetries associated with the 
   incoherent -t bins.}
\label{Table:freeproton-t_bins}
\end{center}
\end{table}

\begin{figure}[h!]
   \centering
   \includegraphics[height=17.0cm]{4D-incoh-bin/4D-t_InCoh_bins.pdf}
   \caption{ First row: the four bins in $t$ of the incoherent DVCS events.  
   Second row: the associated distributions of $Q^2$ for the bins in $t$.  
   Third row: the associated distributions of $x_B$ for the bins in $t$.}
\label{fig:incoh_xB-bins-freep}
\end{figure}

\begin {table}[!h]
\begin{center}
\begin{tabular}{|l|l|l|l|l|l|l|l|}
\hline
<$x_{B}$> & <$Q^2$> & <-t> & $\alpha$ & $\Delta \alpha$ &  $\beta$ & $\Delta 
   \beta$ & $\chi^{2}$\\
\hline
0.177 & 1.56 & 0.14 & 0.190 & 0.009 & -0.03 & 0.12  & 2.3\\
\hline
0.249 & 1.95 & 0.28 & 0.275 & 0.014 & -0.06 & 0.09  & 1.3\\
\hline
0.345 & 2.64 & 0.30 & 0.269 & 0.019 & 0.29 & 0.15  & 0.3\\
\hline
0.471 & 3.34 & 0.78 & 0.262 & 0.052 & -0.23 & 0.25  & 0.9\\
\hline
\end{tabular}
   \caption{Free proton DVCS published asymmetries associated with the 1250 
   incoherent $Q^{2}$ and $x_{B}$ bins.}
\label{Table:freeproton-x_Q2_bins}
\end{center}
\end{table}

\begin{figure}[tp]
\centering
\includegraphics[scale=0.52]{4D-incoh-bin/comp_ALU_ratioInc_Q2_shortscenrario.pdf}\\
\includegraphics[scale=0.52]{4D-incoh-bin/comp_ALU_ratioInc_x_shortscenrario.pdf}\\
\includegraphics[scale=0.52]{4D-incoh-bin/comp_ALU_ratioInc_t_shortscenrario.pdf}
\caption{ The $A_{LU}$ ratio between the bound and the free proton at 
   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
   middle), and $t$ (on the bottom). The black squares are our results using 
   the interpolation method to get the free proton asymmetries at our kinematic 
   , the red squares are our results using the method of tuning our kinematics 
   to get kinematics similar to the published free proton from E1DVCS1 
   experiment. The gray band stands for the systematic errors calculated as the 
   difference between the two extraction methods. The green circles are the 
   HERMES inclusive measurement \cite{HERMES_BSA} results. The blue and red 
   curves are from an on-shell calculations from S.  Liuti and K.  Taneja 
   \cite{simonetta_2}. The solid and dashed black curves are from the off-shell 
   calculations \cite{EMC_vadim_2}.} \label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}

>>>>

\chapter{Binning the incoherent DVCS data to match the free proton DVCS 
published data}
 \label{app_free_proton_4D}

Following the discussion in section \ref{sec:Generalized_EMC} and the 
interpolation technique for the free proton DVCS asymmetries in 
Appendix~\ref{app:free-proton-alu}, here we carry out a different technique to 
validate the calculated incoherent DVCS asymmetry ratios. We apply tuning cuts 
on the kinematical distributions to get similar mean values close to the 
published free proton kinematics published in \ref{fig:FXfree-proton-alu}. For 
instance, regarding the binning in $Q^2$, we start binning our incoherent DVCS 
data into four bins in $Q^2$ with mean values similar to the published free 
proton values, then we apply tuning cuts on the associated distributions in 
$x_B$ and $t$. Figure \ref{fig:incoh_Q2-bins-freep} shows the resulting 
kinematical distributions for the $Q^2$ bins, which are compared to the 
published free proton bins shown in table~\ref{Table:freeproton-x_Q2_bins}.  
Similarly, we apply tuning cuts to the binning in $x_B$ and $-t$ dependence.  
Figure \ref{fig:incoh_xB-bins-freep} shows the resulting kinematical 
distributions for the $x_B$ bins, which are compared to the published free 
proton bins shown in table~\ref{Table:freeproton-x_Q2_bins}. Figure 
\ref{fig:incoh_t-bins-freep} shows the resulting kinematical distributions for 
the $t$ bins, which are compared to the published free proton bins shown in 
table~\ref{Table:freeproton-t_bins}.

The beam-spin asymmetry dependence on $Q^2$, $x_B$, and $t$ bins is constructed 
as a function of the azimuthal angle $\phi$ and fitted for the incoherent DVCS 
data. The $A_{LU}$ ratios at $\phi$~=~90$^{\circ}$ are calculated using the two 
methods; interpolating the free proton data and tunning the incoherent DVCS 
data. The results are presented in 
Figure~\ref{fig:incoh_EMC_ratio_ALU_proton_two}. To conclude, the second method 
provides us with the adequate validation of the extracted asymmetry ratios 
using the interpolation technique. The difference between the two calculated 
asymmetry ratios will be considered as a systematic uncertainty to the first 
method.

@@

\begin{figure}[h!]
   \centering
   \includegraphics[height=17.0cm]{4D-incoh-bin/4D-t_InCoh_bins.pdf}
   \caption{ First row: the four bins in $t$ of the incoherent DVCS events.  
   Second row: the associated distributions of $Q^2$ for the bins in $t$.  
   Third row: the associated distributions of $x_B$ for the bins in $t$.}
\label{fig:incoh_t-bins-freep}
\end{figure}

\begin {table}[!h]
\begin{center}
\begin{tabular}{|l|l|l|l|l|l|l|l|}
\hline
<$x_{B}$> & <$Q^2$> & <-t> & $\alpha$ & $\Delta \alpha$ &  $\beta$ & $\Delta 
   \beta$ & $\chi^{2}$\\
\hline
0.177 & 1.56 & 0.14 & 0.190 & 0.009 & -0.03 & 0.12  & 2.3\\
\hline
0.249 & 1.95 & 0.28 & 0.275 & 0.014 & -0.06 & 0.09  & 1.3\\
\hline
0.345 & 2.64 & 0.30 & 0.269 & 0.019 & 0.29 & 0.15  & 0.3\\
\hline
0.471 & 3.34 & 0.78 & 0.262 & 0.052 & -0.23 & 0.25  & 0.9\\
\hline
\end{tabular}
   \caption{Free proton DVCS published asymmetries associated with the 
   incoherent $Q^{2}$ and $x_{B}$ bins.}
\label{Table:freeproton-x_Q2_bins}
\end{center}
\end{table}

\begin {table}[!h]
\begin{center}
\begin{tabular}{|l|l|l|l|l|l|l|l|}
\hline
<$x_{B}$> & <$Q^2$> & <-t> & $\alpha$ & $\Delta \alpha$ &  $\beta$ & $\Delta 
   \beta$ & $\chi^{2}$\\
\hline
0.238  & 1.89 & 0.14 & 0.243 & 0.013 & -0.02 & 0.09 & 1.0\\
\hline
0.249  & 1.95 & 0.28 & 0.275 & 0.014 & -0.06 & 0.09 & 1.3\\
\hline
0.249  & 1.95 & 0.49 & 0.200 & 0.026 & -0.36 & 0.15 & 1.3\\
\hline
0.248  & 1.94 & 0.77 & 0.172 & 0.035 & 0.01 &  0.31 & 0.3\\
\hline
\end{tabular}
   \caption{Free proton DVCS published asymmetries associated with the 
   incoherent $t$ bins.}
\label{Table:freeproton-t_bins}
\end{center}
\end{table}

\begin{figure}[tp]
\centering
\includegraphics[scale=0.52]{4D-incoh-bin/comp_ALU_ratioInc_Q2_shortscenrario.pdf}\\
\includegraphics[scale=0.52]{4D-incoh-bin/comp_ALU_ratioInc_x_shortscenrario.pdf}\\
\includegraphics[scale=0.52]{4D-incoh-bin/comp_ALU_ratioInc_t_shortscenrario.pdf}
\caption{ The $A_{LU}$ ratio between the bound and the free proton at 
   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
   middle), and $t$ (on the bottom). The black squares are our results using 
   the interpolation method to get the free proton asymmetries at our kinematic 
   , the red squares are our results using the method of tuning our kinematics 
   to get kinematics similar to the published free proton from E1DVCS1 
   experiment. The gray band stands for the systematic errors calculated as the 
   difference between the two extraction methods. The green circles are the 
   HERMES inclusive measurement \cite{HERMES_BSA} results. The blue and red 
   curves are from an on-shell calculations from S.  Liuti and K.  Taneja 
   \cite{simonetta_2}. The solid and dashed black curves are from the off-shell 
   calculations \cite{EMC_vadim_2}.} \label{fig:incoh_EMC_ratio_ALU_proton_two}
\end{figure}

### 2018-08-28 analysis-note-vf/results.tex
update the analysis note

The explored kinematical ranges of $Q^2$, $x_{B}$ and $-t$ of the free-proton 
data are similar to the ones of the incoherent channel, and the two data sets 
were recorded using similar electron-beam energies and experimental setup.  
Therefore, we construct $A_{LU}$ ratios based on choosing the free proton bins 
which have similar $Q^2$, $x_{B}$ and $-t$ values as our bins. The incoherent 
$A_{LU}$ ratios at $\phi$~=~90$^{\circ}$ are shown in figure 
\ref{fig:incoh_EMC_ratio_ALU_proton} as functions of $Q^{2}$, $x_{B}$, and 
$-t$, along with theoretical predictions at similar kinematical values.

>>>>

The explored kinematical ranges of $Q^2$, $x_{B}$ and $-t$ of the free-proton 
data are similar to the ones of the incoherent channel, and the two data sets 
were recorded using similar electron-beam energies and experimental setup. Due 
to the different binning that has been performed over the published free proton 
data, we performed an interpolation to extract the free proton asymmetries at 
the kinematics of our incoherent DVCS bins. In Appendix 
\ref{app:free-proton-alu} we detail this extraction procedure. Additionally, In 
Appendix \ref{app_free_proton_4D} we carried out a different binning procedure 
to our incoherent DVCS binning in order to get an overall validation of the 
interpolated free proton DVCS asymmetries. In each extraction method, the 
$A_{LU}$ ratios have been calculated, and the difference between the two 
methods has been associated as systematic errors to the calculated $A_{LU}$ 
ratios using the interpolation technique. The measured incoherent $A_{LU}$ 
ratios at $\phi$~=~90$^{\circ}$ are shown in figure 
\ref{fig:incoh_EMC_ratio_ALU_proton} as functions of $Q^{2}$, $x_{B}$, and 
$-t$, along with theoretical predictions at similar kinematical values.
